\documentclass[ALICE,manyauthors]{cernphprep}
\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{xspace}

\usepackage[T1]{fontenc} % if needed
\usepackage{setspace}
\usepackage{capt-of}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{multirow}
\usepackage{tabu}
 \usepackage[draft]{todonotes}

\usepackage{tabularx}
\usepackage{changepage}     
\usepackage[figuresright]{rotating}


\newcolumntype{?}{!{\vrule width 2pt}}
\newcolumntype{@}{!{\vrule width 1.5pt}}


\linenumbers
\begin{document}
\input{commands.tex}

%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
% the dates below correspond to CERN approval
% please don't touch: EB chairs will take care
\PHyear{XXXX}       % required, will be obtained from CERN
\PHnumber{XXX}      % required, will be obtained from CERN
\PHdate{Day Month}  % required, will be obtained from CERN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Put your own title + short title here:
\title{Non-linear flow modes of identified particles in Pb--Pb collisions at \sNN}
\ShortTitle{Non-linear flow modes of identified particles in Pb--Pb collisions}   % appears on left page headers

%%% Do not change the next lines
\Collaboration{ALICE Collaboration\thanks{See Appendix~\ref{app:collab} for the list of collaboration members}}
\ShortAuthor{ALICE Collaboration} % appears on right page headers, do not change

\begin{abstract}
\noindent The $p_{\mathrm{T}}$-differential non-linear flow modes, $v_{4,22}$, $v_{5,32}$, $v_{6,33}$ and $v_{6,222}$ for identified particles have been measured for the first time in Pb--Pb collisions at \sNN~with the ALICE detector at the Large Hadron Collider. The results were obtained with a multi-particle correlation technique, namely the generic framework, correlating the identified hadrons with the reference particles from a different pseudorapidity region. The second and third order anisotropic flow coefficients are mostly related to their corresponding initial spatial anisotropy. It has been shown that higher harmonics ($n > 3$) have significant contribution from lower order flow harmonics giving rise to non-linear flow modes in the higher flow harmonics. Thus, these non-linear observables probe the contribution of the second and third order symmetry plane angles in higher flow harmonics. Interestingly, all the characteristic features observed in previous $p_{\mathrm{T}}$-differential measurements (e.g. $v_{2}$ and $v_{3}$) for various particle species are also present in the measurement of the non-linear flow modes , i.e. increase of magnitude by increasing the centrality percentile, mass ordering at low $p_{\mathrm{T}}$ and particle type grouping in the intermediate $p_{\mathrm{T}}$ range. Hydrodynamical calculations (iEBE-VISHNU) that use different initial conditions and values of shear and bulk viscosity to entropy density ratios are confronted with the data at low transverse momenta. This comparison provides increased discriminatory power in the study of initial conditions as well as a new stringent constraint to hydrodynamical calculations.

%The results for \pT~$< 3$ \GeV~are confronted with hydrodynamical model (iEBE-VISHNU) that uses two different initial conditions, one generated by A Multi-Phase Transport model (AMPT) which describes the expansion of the fire using a specific shear viscosity ($\eta/s$) of 0.08 and specific bulk viscosity ($\zeta/s$) of zero, coupled to a hadronic cascade model (UrQMD) and the other generated by TRENTo (Reduced Thickness Event-by-event Nuclear Topology) which uses a temperature dependent specific shear and bulk viscosity. 


\end{abstract}
\end{titlepage}

\setcounter{page}{2} %please do not remove this line
\tableofcontents
\newpage
\setcounter{page}{3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% begin main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/introduction.tex}
\input{sections/experimentalSetup.tex}
\input{sections/analysisdetails.tex}
\input{sections/flowMethods.tex}
\input{sections/systematics.tex}
\input{sections/results.tex}
\input{sections/conclusion.tex}
%\input{sections/appendix.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% end main text 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% acknowledgements - handled by EB chairs 
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
% add specific acknowledgements here 
% ...but please don't remove the line below: funding agencies
% will be acknowledged with a custom tex file handled by EB chairs after Collab Round 2
%\input{acknowledgements.tex}
\end{acknowledgement}

\newpage

%%%%%%%% Bibliography 
\bibliographystyle{utphys}   % Remember we use title in the biblio
\bibliography{bibliography}
%\input {bibliography.bib}  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices: yours (if any) + authorlist
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\input{appendix.tex}

%
%\input{} % put your appendices here (if any)
%

%%%%% Authorlist - please do not touch: handled by EB chairs 
\section{The ALICE Collaboration}
\label{app:collab}
%\input{authorlist-preprint.tex}  
\end{document}